### 2018-12-18 README.Rmd
add todo chunk for animal data

* [x] IWS pasture types (forage or not)
* [x] IWS specific crops (corn, wheat, etc.)
* [ ] IWS crop frequency/rotation
</p></details>

@@

* [x] IWS wetland potential (as a proxy for tile drainage)
* [x] IWS soil organic carbon
* [ ] IWS root zone depth
* [ ] IWS lithology (sand %, clay %, etc.)
</p></details>

@@

* [x] Lake depth
* [x] IWS area
* [x] IWS/Lake area
* [x] TP, TN, NO3
</p></details>

>>>>

* [x] IWS pasture types (forage or not)
* [x] IWS specific crops (corn, wheat, etc.)
* [ ] ~IWS crop frequency/rotation~ -AK says this is probably not needed
</p></details>

@@

* [x] IWS wetland potential (as a proxy for tile drainage)
* [x] IWS soil organic carbon
* [ ] IWS bulk density - needed to compute soil carbon mass
* [ ] IWS rock content - needed to compute soil carbon mass
* [ ] IWS root zone depth
* [ ] IWS lithology (sand %, clay %, etc.)
</p></details>

@@

* [x] Lake depth
* [x] IWS area
* [x] IWS/Lake area
* [x] TP, TN, NO3
* [ ] IWS precip variability
  * the area of a given crop in year n-1 matters. Usually, dry years leave nutrients on the ground, and when followed up by a wet year you get the largest signal in year n.
</p></details>

<details><summary>Animal data</b> (`USDA Census`) </summary><p>

* [ ] Animal units
</p></details>
